Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem

### 2017-01-11 manuscript.tex
Use JAS style
Issue #1

\documentclass[preprint]{elsarticle}

\usepackage{acta_astronautica_packages} % packages and referencing customization
\input{macros} % defines custom macros

\journal{Acta Astronautica}

@@

\begin{frontmatter}

@@

%% Group authors per affiliation:
\author[gwu_address]{Shankar Kulumani\fnref{kulumanifootnote}\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{skulumani@gwu.edu}

\author[gwu_address]{Taeyoung Lee\fnref{leefootnote}}
\ead{tylee@gwu.edu}

\fntext[kulumanifootnote]{Doctoral Student, Mechanical and Aerospace Engineering} 
\fntext[leefootnote]{Associate Professor, Mechanical and Aerospace Engineering}

\address[gwu_address]{George Washington University, 800 22nd St NW, Washington, DC 20052\\ Tel: 202-994-6749}

@@

\begin{keyword}
Low-thrust, Reachability, Optimal Control, Variational Integrator
\end{keyword}

\end{frontmatter}

@@

\bibliography{library}
\bibliographystyle{elsarticle-num}
\end{document}

>>>>

\documentclass[letterpaper, submit]{AAS}

\usepackage{jas_packages} % packages and referencing customization
\input{macros} % defines custom macros

@@

@@

\author{Shankar Kulumani\thanks{Doctoral Student, Mechanical \& Aerospace Engineering, George Washington University, 800 22nd St NW, Washington, DC 20052.},  
Taeyoung Lee\thanks{Associate Professor, Mechanical \& Aerospace Engineering, George Washington University, 800 22nd St NW, Washington, DC 20052.}
}

\maketitle{}

@@

@@

\bibliography{library}
\bibliographystyle{AAS_publication}
\end{document}
